Methods paper for erosion

### 2017-11-08 docs/methods/erosion_methods.tex
Just realized that my trapezoid rule for computing the integrating factor is only 2nd order in time, so it makes no sense to use RK4. I should just use RK2 so that everything is second order in time.

For simplicity, we introduce the variables
\begin{align}
\label{eq:M}
& M = - \mean{\thalpha \Vn} \\
\label{eq:N}
& N = \frac{1}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
& \elfun = \frac{1}{L^{2} \log \left(2\pi/L \right)}
\end{align} 
Then Eq.~(\ref{eqn:thetaevo0}) can be rewritten as
\begin{equation}
\label{eqn:thetaevo1}
\pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + N
\end{equation}
Note that the $\elfun$ depends only on $L(t)$, and so the highest order derivative in Eq.~(\ref{eqn:thetaevo1}) is {\em linear} in the variable $\alpha$. This is the key to the {\thL} method, and allows us to use very stable, implicit methods for the stiff term. We will evolve $\theta$ in spectral space, and so introduce the transforms
\begin{align}
& \theta(\alpha,t) = \sum_{k = -\infty}^{\infty} \thhat_k e^{2\pi i k \alpha} \\
& N(\alpha,t)  = \sum_{k = -\infty}^{\infty} \hat{N}_k e^{2\pi i k \alpha}
\end{align}
Equation (\ref{eqn:thetaevo1}) gives a set of ODEs for the coefficients
\begin{equation}
\tderiv{\thhat_k}{t} +  4 \eps \pi^2 k^2  \elfun \thhat_k = \hat{N}_k
\end{equation}
We introduce the integrating factor
\begin{equation}
\label{eq:mu}
\mu_k = \exp \left( 4 \eps \pi^2 k^2 \int \elfun \, dt \right)
\end{equation}
Then the evolution equations for $L$ and $\theta$ can be recast as the coupled system of ODEs
\begin{align}
\label{eqn:Levo2}
& \tderiv{L}{t} = M \\
\label{eqn:thetaevo2}
& \tderiv{}{t}\left( \mu_k \theta_k \right) = \mu_k \hat{N}_k
\end{align}
We solve system (\ref{eqn:Levo2})--(\ref{eqn:thetaevo2}) for the variables $L$ and $\{ \mu_k \theta_k \}$ with a 4th-order Runge-Kutta method. At each stage, we must recover $\theta(\alpha,t)$ from  $\{ \mu_k \theta_k \}$ in order to compute the shear stress as needed in Eqs.~(\ref{eq:M}) and (\ref{eq:N}) for $M$ and $N$. For this, we compute $\mu_k$ from Eq.~(\ref{eq:mu}) using the trapezoid rule, then recover $\theta(\alpha, t)$ via a Gaussian filter....

>>>>

For simplicity, we introduce the variables
\begin{align}
\label{eq:M}
& M = - \mean{\thalpha \Vn} \\
\label{eq:N}
& N = \frac{1}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
& \elfun = \frac{1}{L^{2} \log \left(2\pi/L \right)}
\end{align} 
Then Eq.~(\ref{eqn:thetaevo0}) can be rewritten as
\begin{equation}
\label{eqn:thetaevo1}
\pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + N
\end{equation}
Note that the $\elfun$ depends only on $L(t)$, and so the highest order derivative in Eq.~(\ref{eqn:thetaevo1}) is {\em linear} in the variable $\alpha$. This is the key to the {\thL} method, and allows us to use very stable, implicit methods for the stiff term. We will evolve $\theta$ in spectral space, and so introduce the transforms
\begin{align}
& \theta(\alpha,t) = \sum_{k = -\infty}^{\infty} \thhat_k e^{2\pi i k \alpha} \\
& N(\alpha,t)  = \sum_{k = -\infty}^{\infty} \hat{N}_k e^{2\pi i k \alpha}
\end{align}
Equation (\ref{eqn:thetaevo1}) gives a set of ODEs for the coefficients
\begin{equation}
\tderiv{\thhat_k}{t} +  4 \eps \pi^2 k^2  \elfun \thhat_k = \hat{N}_k
\end{equation}
We introduce the integrating factor
\begin{equation}
\label{eq:mu}
\mu_k = \exp \left( 4 \eps \pi^2 k^2 \int \elfun \, dt \right)
\end{equation}
Then the evolution equations for $L$ and $\theta$ can be recast as the coupled system of ODEs
\begin{align}
\label{eqn:Levo2}
& \tderiv{L}{t} = M \\
\label{eqn:thetaevo2}
& \tderiv{}{t}\left( \mu_k \theta_k \right) = \mu_k \hat{N}_k
\end{align}
We solve system (\ref{eqn:Levo2})--(\ref{eqn:thetaevo2}) for the variables $L$ and $\{ \mu_k \theta_k \}$ with a 2nd-order Runge-Kutta method. At each stage, we must recover $\theta(\alpha,t)$ from  $\{ \mu_k \theta_k \}$ in order to compute the shear stress as needed in Eqs.~(\ref{eq:M}) and (\ref{eq:N}) for $M$ and $N$. For this, we compute $\mu_k$ from Eq.~(\ref{eq:mu}) using the trapezoid rule, then recover $\theta(\alpha, t)$ via a Gaussian filter....
